---
title: "individual1"
author: "Jaeyeon Won"
date: "9/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Reading in the data set
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 

#Information
str(choco) 
```

## Searching for the Best Chocolates
We will be exploring what aspects of the chocolates may affect taste. Before setting off to the exploration, answer the following questions.

1. How are the ratings distributed? Create both a histogram and a boxplot and describe them. Don’t forget to mention outliers, if there are any.
```{r}
#Histogram
hist(choco$Rating,
     xlim = c(1,5),
     main = 'Histogram of Rating',
     xlab = 'Rating')

#Boxplot
boxplot(choco$Rating,
        main = 'Boxplot of Rating',
        xlab = 'Rating')
```

The rating of chocolates is on the scale from 1.0 to 5.0 where (1.0-1.9) is for 'Unpleasant', 
(2.0-2.9) is for 'Disappointing', (3.0-3.49) is for 'Recommended', (3.5-3.9) is for 'Highly Recommended', and (4.0-5.0) is for 'Outstanding'. According to the histogram and boxplot, the distribution of chocolates is a little bit skewed to the left and bimodal with multiple outliers in the lower range below a rating of 2.0. A lot of chocolates are concentrated in the higher rating range of 'Disappointing'(2.6-2.9), higher rating range of 'Recommended' (3.2-3.49), and lower rating range of 'Highly Recommended' (3.5-3.6).One interesting feature is that there was no chocolate with a rating between 3.0 and 3.24 as well as above 4.0. More specifically about the baxplot, the lowest score was 1.0, the highest score was 4.0, and the median score was around 3.25.


2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
```{r}
#Changing the type of Date variable (from integer to factor)
year = as.factor(choco$Date)
str(year)

#Checking the distribution of each level
table(year)

#Barplot
barplot(table(year),
        main = 'Barplot of the Number of Ratings in Each Year',
        xlab = 'Year',
        ylab = 'Number of Ratings',
        horiz = TRUE,
        las = 1)
```
Based on the barplot above, 2015 has the most rating counts. Conversely, 2020 has the least number of ratings, which makes sense because 2020 has not passed yet and we still have 4 months left until the end of 2020. There was an increasing trend on the number of ratings from 2006 to 2015. Since 2015, there has been a decreasing trend until now. In 2017, there was relatively few reports on the ratings.

3. Do ratings depend on the cacao percentage of a chocolate bar? Create both numerical and graphical summaries, and explain.
```{r}
#Numerical Summary
#Subsetting
Unpleasant = choco[(choco$Rating >= 1.0) & (choco$Rating <= 1.9), ]
Disappointing = choco[(choco$Rating >= 2.0) & (choco$Rating <= 2.9), ]
Recommended = choco[(choco$Rating >= 3.0) & (choco$Rating <= 3.49), ]
HighlyRecommended = choco[(choco$Rating >= 3.5) & (choco$Rating <= 3.9), ]
Outstanding = choco[(choco$Rating >= 4.0) & (choco$Rating <= 5.0), ]
#Saving the average cocoa percent for each subset in a vector
mean_cocoa_percent = c(mean(Unpleasant$Cocoa_Percent), 
                       mean(Disappointing$Cocoa_Percent), 
                       mean(Recommended$Cocoa_Percent), 
                       mean(HighlyRecommended$Cocoa_Percent), 
                       mean(Outstanding$Cocoa_Percent))


plot(choco$Cocoa_Percent, choco$Rating, 
     main = "Scatterplot of Cacao Percent and Ratings",
     xlab = "Cocoa Percent", ylab = "Ratings")
```


Now, we are ready to explore.

4. How do different characteristics of the chocolate compare? To elaborate, which characteristics tend to be more favorable and which ones are not? Create both numerical and graphical summaries, and explain.
```{r}
```

5. Brainstorm two analyses you would like to perform with your teammate. Describe in plain language what comparisons are you making. Create suitable numerical and graphical summaries for your analyses. Describe the results.
  + How do chocolates have different ratings for different locations? (Here, we are comparing )
```{r}
```
  
  + How do chocolates have different ratings for different bean origins?

