---
title: "Lab2Investigation"
output: html_document
---

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco)
```

Part 1.<br />
Based on the histogram, ratings are fairly left skewed resulting in higher than average ratings for the chocolates, there are though a couple outliers around the 'one' rating.
```{r}
boxplot(choco$Rating, main="Boxplot of Chocolate Ratings")
hist(choco$Rating, breaks = 10, main="Histogram of Chocolate Ratings", xlab="Rating", ylab="Occurance")
```

Part 2.<br />
Throughout every year the average ratings are around a 3.
```{r}
barplot(choco$Rating, choco$Date)
```

Part 3.<br />
There doesn't appear to be a trivial trend when comparing cocoa percent with rating. You could argue that a cocoa percent that is too high, or too low would receieve a slightly lower rating.
```{r}
plot(choco$Cocoa_Percent, choco$Rating)
```

Part 4.<br />
Characteristics4 seems to vary the most between ratings. Characteristics 1-3 all have a general trend of ratings around the 3-3.5 mark and some outliers.
```{r}
boxplot(choco$Rating ~ choco$Characteristics1)
boxplot(choco$Rating ~ choco$Characteristics2)
boxplot(choco$Rating ~ choco$Characteristics3)
boxplot(choco$Rating ~ choco$Characteristics4)
```
Part 5.<br />
I would like to see how Cocoa percent compares to dates of chocolate. I wonder if throughout the years cocoa percent has increased, decreased or stayed the same.
I would also like to see how rating compares to bean origin. It would be intersting to see what parts of the world produced higher rated chocolate.
```{r}
plot(choco$Date, choco$Cocoa_Percent)
```
It is interesting to see how the cocoa percentage settled down and became less extreme towards the end of the 2010's and didnt have an extremely low values and extremely high values.
```{r}
boxplot(choco$Rating ~ choco$Bean_Origin)
```
This analysis didn't have as interesting of a conclusion as it almost felt arbitrary to where the bean was from. The ratings were fairly consistent between countries and regions.
